{[}1{]} J. Hübotter, F. Lübeck, L. Behric, A. Baumann, M. Bagatella, D.
Marta, I. Hakimi, I. Shenfeld, T. Kleine Buening, C. Guestrin, A.
Krause, ``Reinforcement Learning via Self-Distillation,''
arXiv:2601.20802, 2026. Code: github.com/lasgroup/SDPO. {[}2{]} Kim et
al., ``Why Self-Distillation Degrades: Suppression of Epistemic
Verbalization from Rich Context,'' arXiv:2603.24472, 2026. {[}3{]} I.
Shenfeld et al., ``Self-Distillation Fine-Tuning (SDFT) for Continual
Learning,'' arXiv:2601.19897, 2026. {[}4{]} lasgroup, ``SDPO official
codebase (verl fork),'' github.com/lasgroup/SDPO, 2026. (scientific
reference; KL config α=1.0, top-K=20 cho LCBv6). {[}5{]} HuggingFace,
``TRL v1.4.0 --- SDPO/SDFT Trainer documentation,'' 2026. {[}6{]} N.
Jain, K. Han, A. Gu, W.-D. Li, F. Yan, T. Zhang, S. Wang, A.
Solar-Lezama, K. Sen, and I. Stoica, ``LiveCodeBench: Holistic and
Contamination-Free Evaluation of Large Language Models for Code,''
arXiv:2403.07974, 2024. {[}7{]} Qwen Team, ``Qwen3 Technical Report,''
arXiv:2505.09388, 2025. {[}8{]} Z. Shao et al., ``DeepSeekMath: Pushing
the Limits of Mathematical Reasoning in Open Language Models,''
arXiv:2402.03300, 2024. (introduces GRPO.) {[}9{]} M. Chen et al.,
``Evaluating Large Language Models Trained on Code,'' arXiv:2107.03374,
2021. (pass@k.) {[}10{]} MathArena, ``AIME 2026,'' HuggingFace dataset
\texttt{MathArena/aime\_2026}, 2026. URL:
https://huggingface.co/datasets/MathArena/aime\_2026. {[}11{]} R.
Agarwal et al., ``On-Policy Distillation of Language Models: Learning
from Self-Generated Mistakes,'' arXiv:2306.13649, 2023. (GKD;
generalized JSD, cited by Hübotter for JSD stability.) {[}12{]} E. D.
Dolan and J. J. Moré, ``Benchmarking optimization software with
performance profiles,'' Math. Program., vol.~91, no. 2, pp.~201--213,
2002. (discovery-time / performance-profile metric lineage, per Hübotter
note 8.) {[}13{]} G. Hinton, O. Vinyals, and J. Dean, ``Distilling the
Knowledge in a Neural Network,'' arXiv:1503.02531, 2015.
(knowledge-distillation lineage anchor.)
