\chapter{Chapter 6 --- Limitations and Publication Roadmap}\label{chapter-6-limitations-and-publication-roadmap}

\section{6.1 Methodological Rigor and Validations}\label{methodological-rigor-and-validations}

To ensure the empirical soundness of this study, several critical architectural enhancements and validation metrics have been systematically integrated into the evaluation framework:

\begin{itemize}
\tightlist
\item
  \textbf{Statistical power.} Rather than relying on a localized sign test, this work deploys a medium-scale evaluation framework ($\approx$16 problems $\times$ 6 seeds) combined with a Wilcoxon signed-rank test. This allows the primary treatment effect to be reported with a controlled, mathematically rigorous error rate rather than as a purely directional signal (§4.2).
\item
  \textbf{Compute matching.} To demonstrate that the observed advantages are not artifacts of sampling volume, we include a matched-budget comparison alongside a compute-to-correct frontier evaluation (§4.2.5). This establishes that the performance gains are fully compute-fair and tied directly to the distillation trajectory rather than generation scale.
\item
  \textbf{Granular reasoning evaluation.} Running the complex code optimization arm with reasoning traces enabled (\emph{thinking ON}) provides a complete set of language-based reasoning traces. This transitions the investigation of epistemic verbalization from an isolated mathematical pilot into a measurable, domain-specific empirical result (§4.5).
\item
  \textbf{Exact filtering mechanics.} The removal of the keep-best-correct fallback ensures that the anti-leak filter remains mathematically exact (§4.4, §4.7). The semantic judge is never bypassed, eliminating hidden pipeline interventions during initial optimization cycles.
\item
  \textbf{Confound isolation.} By enforcing a uniform reasoner architecture across distinct domains and introducing the MATH-500 worked-solution dataset, this framework successfully decouples base model capabilities from privileged reference content. This isolates the core drivers of optimization failure in mathematical contexts and directly validates the value-versus-procedure boundary (§4.6).
\end{itemize}

\section{6.2 Scope and Remaining Limitations}\label{scope-and-remaining-limitations}

A transparent academic evaluation requires delineating the structural constraints that persist within this empirical framework:

\begin{itemize}
\tightlist
\item
  \textbf{Model and scale constraints.} All experimental findings are established utilizing a 4B-scale Qwen model evaluated within a personal compute resource allocation. Consequently, these outcomes serve as an empirical characterization within a specific architecture family rather than a universal scaling law or an industry-scale benchmark.
\item
  \textbf{Margin sensitivity to base capability.} As base model capability scales (e.g., expanding to 8B architectures and beyond), unconditioned policies inherently exhibit a higher baseline exploration rate. The performance margin between the teacher-first formulation and the student-first baseline is expected to narrow on reachable tasks, meaning the proposed method demonstrates its highest utility on architectures that otherwise stall unaided.
\item
  \textbf{Confounding of reward shape and content.} In this setup, programming tasks are characterized by both a graded reward and method-bearing references, while the foundational mathematical tasks are governed by a binary reward and value-only feedback. Even with the integration of MATH-500, these structural factors remain partially co-variant unless an explicit cross-domain control (such as graded mathematical testing) is engineered.
\item
  \textbf{Generality of epistemic behavior.} The measurements regarding the suppression of uncertainty markers are tied to a singular model family and a predefined lexical marker set. The generalizability of these behavioral adjustments across disparate tokenizers, model scales, and implicit reasoning styles requires further empirical scaling.
\end{itemize}

\section{6.3 Publication Roadmap}\label{publication-roadmap}

The empirical pipeline developed in this thesis is structured to support peer-reviewed conference dissemination post-graduation. The execution sequence is partitioned into foundational and scaling phases:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Complete the medium-scale matched baseline evaluation and generate the definitive compute-to-correct frontier to secure the core empirical headline.
\item
  Finalize the evaluation of the code generation arm with thinking traces enabled to mathematically finalize the quantification of epistemic suppression (§4.5).
\item
  Execute the comparative MATH-500 worked-solution pipeline utilizing the identical reasoning backbone to formally cement the value-versus-procedure boundary.
\item
  Scale the foundational experiments to an 8B model architecture to formally characterize the interaction between base model capability and self-distillation efficiency.
\item
  Extend testing protocols to a secondary validation code benchmark to verify cross-contamination resistance and algorithmic robustness.
\end{enumerate}

Steps (1) through (3) establish the necessary empirical baseline for submission, while steps (4) and (5) serve as high-utility expansions optimized for personal compute constraints.