\renewcommand{\bibname}{References}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}

\bibitem{r1} Jonas Hübotter, Fabian Lübeck, Leander Behric, Alexander Baumann, Marco Bagatella, Daniel Marta, Ido Hakimi, Idan Shenfeld, Thomas Kleine Buening, Carlos Guestrin, and Andreas Krause, ``Reinforcement Learning via Self-Distillation,'' arXiv:2601.20802, 2026. \url{https://arxiv.org/abs/2601.20802}. Code: \url{https://github.com/lasgroup/SDPO}.

\bibitem{r2} Jeonghye Kim, Xufang Luo, Minbeom Kim, Sangmook Lee, Dohyung Kim, Jiwon Jeon, Dongsheng Li, and Yuqing Yang, ``Why Does Self-Distillation (Sometimes) Degrade the Reasoning Capability of LLMs?,'' arXiv:2603.24472, 2026. \url{https://arxiv.org/abs/2603.24472}.

\bibitem{r3} Idan Shenfeld, Mehul Damani, Jonas Hübotter, and Pulkit Agrawal, ``Self-Distillation Enables Continual Learning,'' arXiv:2601.19897, 2026. \url{https://arxiv.org/abs/2601.19897}.

\bibitem{r4} lasgroup, ``SDPO official codebase (verl fork),'' 2026. \url{https://github.com/lasgroup/SDPO}. (Scientific reference; KL config $\alpha=1.0$, top-$K=20$ for LCBv6.)

\bibitem{r5} HuggingFace, ``TRL v1.4.0 --- SDPO/SDFT Trainer documentation,'' 2026. \url{https://huggingface.co/docs/trl}.

\bibitem{r6} Naman Jain, King Han, Alex Gu, Wen-Ding Li, Fanjia Yan, Tianjun Zhang, Sida Wang, Armando Solar-Lezama, Koushik Sen, and Ion Stoica, ``LiveCodeBench: Holistic and Contamination Free Evaluation of Large Language Models for Code,'' in \emph{Proc. International Conference on Learning Representations (ICLR)}, 2025.

\bibitem{r7} An Yang, Anfeng Li, Baosong Yang, Beichen Zhang, Binyuan Hui, Bo Zheng, Bowen Yu, Chang Gao, Chengen Huang, Chenxu Lv, Chujie Zheng, Dayiheng Liu, Fan Zhou, Fei Huang, Feng Hu, Hao Ge, Haoran Wei, Huan Lin, Jialong Tang, Jian Yang, Jianhong Tu, Jianwei Zhang, Jianxin Yang, Jiaxi Yang, Jing Zhou, Jingren Zhou, Junyang Lin, Kai Dang, Keqin Bao, Kexin Yang, Le Yu, Lianghao Deng, Mei Li, Mingfeng Xue, Mingze Li, Pei Zhang, Peng Wang, Qin Zhu, Rui Men, Ruize Gao, Shixuan Liu, Shuang Luo, Tianhao Li, Tianyi Tang, Wenbiao Yin, Xingzhang Ren, Xinyu Wang, Xinyu Zhang, Xuancheng Ren, Yang Fan, Yang Su, Yichang Zhang, Yinger Zhang, Yu Wan, Yuqiong Liu, Zekun Wang, Zeyu Cui, Zhenru Zhang, Zhipeng Zhou, and Zihan Qiu, ``Qwen3 Technical Report,'' arXiv:2505.09388, 2025. \url{https://arxiv.org/abs/2505.09388}.

\bibitem{r8} Zhihong Shao, Peiyi Wang, Qihao Zhu, Runxin Xu, Junxiao Song, Xiao Bi, Haowei Zhang, Mingchuan Zhang, Y. K. Li, Y. Wu, and Daya Guo, ``DeepSeekMath: Pushing the Limits of Mathematical Reasoning in Open Language Models,'' arXiv:2402.03300, 2024. \url{https://arxiv.org/abs/2402.03300}.

\bibitem{r9} Mark Chen, Jerry Tworek, Heewoo Jun, Qiming Yuan, Henrique Ponde de Oliveira Pinto, Jared Kaplan, Harri Edwards, Yuri Burda, Nicholas Joseph, Greg Brockman, Alex Ray, Raul Puri, Gretchen Krueger, Michael Petrov, Heidy Khlaaf, Girish Sastry, Pamela Mishkin, Brooke Chan, Scott Gray, Nick Ryder, Mikhail Pavlov, Alethea Power, Lukasz Kaiser, Mohammad Bavarian, Clemens Winter, Philippe Tillet, Felipe Petroski Such, Dave Cummings, Matthias Plappert, Fotios Chantzis, Elizabeth Barnes, Ariel Herbert-Voss, William Hebgen Guss, Alex Nichol, Alex Paino, Nikolas Tezak, Jie Tang, Igor Babuschkin, Suchir Balaji, Shantanu Jain, William Saunders, Christopher Hesse, Andrew N. Carr, Jan Leike, Josh Achiam, Vedant Misra, Evan Morikawa, Alec Radford, Matthew Knight, Miles Brundage, Mira Murati, Katie Mayer, Peter Welinder, Bob McGrew, Dario Amodei, Sam McCandlish, Ilya Sutskever, and Wojciech Zaremba, ``Evaluating Large Language Models Trained on Code,'' arXiv:2107.03374, 2021. \url{https://arxiv.org/abs/2107.03374}.

\bibitem{r10} MathArena, ``AIME 2026,'' HuggingFace dataset \texttt{MathArena/aime\_2026}, 2026. \url{https://huggingface.co/datasets/MathArena/aime_2026}.

\bibitem{r11} Rishabh Agarwal, Nino Vieillard, Yongchao Zhou, Piotr Stanczyk, Sabela Ramos, Matthieu Geist, and Olivier Bachem, ``On-Policy Distillation of Language Models: Learning from Self-Generated Mistakes,'' in \emph{Proc. International Conference on Learning Representations (ICLR)}, 2024.

\bibitem{r12} Elizabeth D. Dolan and Jorge J. Moré, ``Benchmarking optimization software with performance profiles,'' \emph{Mathematical Programming}, vol.~91, no.~2, pp.~201--213, 2002.

\bibitem{r13} Geoffrey Hinton, Oriol Vinyals, and Jeff Dean, ``Distilling the Knowledge in a Neural Network,'' arXiv:1503.02531, 2015. \url{https://arxiv.org/abs/1503.02531}.

\bibitem{r14} John Schulman, Filip Wolski, Prafulla Dhariwal, Alec Radford, and Oleg Klimov, ``Proximal Policy Optimization Algorithms,'' arXiv:1707.06347, 2017. \url{https://arxiv.org/abs/1707.06347}.

\bibitem{r15} Long Ouyang, Jeff Wu, Xu Jiang, Diogo Almeida, Carroll L. Wainwright, Pamela Mishkin, Chong Zhang, Sandhini Agarwal, Katarina Slama, Alex Ray, John Schulman, Jacob Hilton, Fraser Kelton, Luke Miller, Maddie Simens, Amanda Askell, Peter Welinder, Paul Christiano, Jan Leike, and Ryan Lowe, ``Training Language Models to Follow Instructions with Human Feedback,'' in \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2022.

\bibitem{r16} Rafael Rafailov, Archit Sharma, Eric Mitchell, Stefano Ermon, Christopher D. Manning, and Chelsea Finn, ``Direct Preference Optimization: Your Language Model is Secretly a Reward Model,'' in \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2023.

\bibitem{r17} Jason Wei, Xuezhi Wang, Dale Schuurmans, Maarten Bosma, Brian Ichter, Fei Xia, Ed Chi, Quoc Le, and Denny Zhou, ``Chain-of-Thought Prompting Elicits Reasoning in Large Language Models,'' in \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2022.

\bibitem{r18} Xuezhi Wang, Jason Wei, Dale Schuurmans, Quoc Le, Ed Chi, Sharan Narang, Aakanksha Chowdhery, and Denny Zhou, ``Self-Consistency Improves Chain of Thought Reasoning in Language Models,'' in \emph{Proc. International Conference on Learning Representations (ICLR)}, 2023.

\bibitem{r19} Eric Zelikman, Yuhuai Wu, Jesse Mu, and Noah D. Goodman, ``STaR: Bootstrapping Reasoning With Reasoning,'' in \emph{Advances in Neural Information Processing Systems (NeurIPS)}, 2022.

\bibitem{r20} Bradley Brown, Jordan Juravsky, Ryan Ehrlich, Ronald Clark, Quoc V. Le, Christopher Ré, and Azalia Mirhoseini, ``Large Language Monkeys: Scaling Inference Compute with Repeated Sampling,'' arXiv:2407.21787, 2024. \url{https://arxiv.org/abs/2407.21787}.

\bibitem{r21} Niklas Muennighoff, Zitong Yang, Weijia Shi, Xiang Lisa Li, Li Fei-Fei, Hannaneh Hajishirzi, Luke Zettlemoyer, Percy Liang, Emmanuel Candès, and Tatsunori Hashimoto, ``s1: Simple Test-Time Scaling,'' arXiv:2501.19393, 2025. \url{https://arxiv.org/abs/2501.19393}.

\bibitem{r22} Hunter Lightman, Vineet Kosaraju, Yura Burda, Harri Edwards, Bowen Baker, Teddy Lee, Jan Leike, John Schulman, Ilya Sutskever, and Karl Cobbe, ``Let's Verify Step by Step,'' in \emph{Proc. International Conference on Learning Representations (ICLR)}, 2024.

\bibitem{r23} Saurav Kadavath, Tom Conerly, Amanda Askell, Tom Henighan, Dawn Drain, Ethan Perez, Nicholas Schiefer, Zac Hatfield-Dodds, Nova DasSarma, Eli Tran-Johnson, Scott Johnston, Sheer El-Showk, Andy Jones, Nelson Elhage, Tristan Hume, Anna Chen, Yuntao Bai, Sam Bowman, Stanislav Fort, Deep Ganguli, Danny Hernandez, Josh Jacobson, Jackson Kernion, Shauna Kravec, Liane Lovitt, Kamal Ndousse, Catherine Olsson, Sam Ringer, Dario Amodei, Tom Brown, Jack Clark, Nicholas Joseph, Ben Mann, Sam McCandlish, Chris Olah, and Jared Kaplan, ``Language Models (Mostly) Know What They Know,'' arXiv:2207.05221, 2022. \url{https://arxiv.org/abs/2207.05221}.

\bibitem{r24} Yoon Kim and Alexander M. Rush, ``Sequence-Level Knowledge Distillation,'' in \emph{Proc. Empirical Methods in Natural Language Processing (EMNLP)}, 2016, pp.~1317--1327.

\end{thebibliography}
